---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# blizz

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/tyluRp/blizz.svg?branch=master)](https://travis-ci.org/tyluRp/blizz)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/tyluRp/blizz?branch=master&svg=true)](https://ci.appveyor.com/project/tyluRp/blizz)
[![Codecov test coverage](https://codecov.io/gh/tyluRp/blizz/branch/master/graph/badge.svg)](https://codecov.io/gh/tyluRp/blizz?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

Minimalistic client to access [Blizzards API](https://develop.battle.net/).

## Installation

You can install from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tyluRp/blizz")
```

## Additional Setup

Installing the package alone isn't enough to get started. You will need to create a developer account at Blizzards new [dev portal](https://develop.battle.net/). Once you've created an account, a client needs to be made. Creating a client will produce a **Client ID** and **Client Secret**. With these credentials you can simply run:

```r
blizz_creds("your_client_id", "your_client_secret")
```

This will do a couple things:

1. Store the Client ID and Secret in the `.Renviron` file. If you don't have one, it'll create one for you.
2. Run a system command to produce an **authentication token** which is then stored in `.Renviron`.

After this, you're all set. 

However, I realize that allowing some stranger (i.e. me) to modify your `.Renviron` is scary! If you want to avoid using `blizz_creds()`, you can obtain the client ID, secret, and token by following the [docs](https://develop.battle.net/documentation/guides/getting-started). Then edit the `.Renviron` file manually and supply the credentials like so:

```r
BLIZZARD_CLIENT_ID='your ID'
BLIZZARD_CLIENT_SECRET='your secret'
BLIZZARD_AUTH_TOKEN='your token'
```

Note that Blizzards authentication tokens expire after 24 hours. To refresh the authentication token run the following:

```r
blizz_creds(refresh = TRUE)
```

This will remove the expired token from your `.Renviron` and add the fresh token to it. Additionally it will run `Sys.setenv("your_new_token")` to avoid having to restart the R session.

## Example

Use the `blizz()` function to access all API endpoints. Note that the leading slash must be included as well:

```{r example1}
library(blizz)
library(dplyr, warn.conflicts = FALSE)
library(tidyr)
library(janitor)

# Here's one example of extracting the StarCraft II grandmaster ladder
blizz("/sc2/ladder/grandmaster/1?") %>% 
  .[["ladderTeams"]] %>% 
  unnest() %>% 
  as_tibble() %>% 
  clean_names("snake") %>% 
  select(display_name, clan_tag, favorite_race, mmr, wins, losses, points)
```

When making a request you pretty much need to copy and paste everything in-between the request URL and the access token. In the example above, we needed `/sc2/ladder/grandmaster/1?`. 

Additionally, we can print the response as JSON thanks to the [`jsonlite`](https://github.com/jeroen/jsonlite) package:

```{r example2}
blizz("/d3/data/act/1?locale=en_US&", json = TRUE)
```
