---
title: "Recipes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{recipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a work in progress vignette meant to provide a set of recipes for taking `blizz` data and formatting it into a dataframe. The sections will be split into three, World of Warcraft, StarCraft, and Diablo. Each game gets its own recipe section.

```{r, message=FALSE}
library(blizz)
library(dplyr)
library(tidyr)
library(purrr)
```

## Diablo 3

See the Diablo 3 community API reference [here](https://develop.battle.net/documentation/api-reference/diablo-3-community-api) for more information.

### Diablo 3 Act API

#### `getActIndex`

Returns an index of acts.

```{r}
blizz("/d3/data/act") %>% 
  .[["acts"]] %>%
  .[["quests"]] %>% 
  bind_rows(.id = "act") %>% 
  unnest() %>% 
  as_tibble()
```

#### `getAct`

Returns a single act by ID.

```{r}
blizz("/d3/data/act/1") %>% 
  .[["quests"]] %>% 
  as_tibble() %>% 
  unnest()
```

### D3 Artisan and Recipe API

#### `getArtisan`

Returns a single artisan by slug.

#### `getRecipe`

Returns a single recipe by slug for the specified artisan.

## StarCraft II

## World of Warcraft




